---
title: "202-species-tree"
author: "Mac Campbell"
date: "3/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

## Species Tree

### Get meta and make groups

```{r}
b4<-read_tsv("outputs/200/b4.tsv")
write_tsv(b4 %>% select(`Sample ID`), "outputs/200/samples260.tsv", col_names = FALSE)
```

```{r}
deets <- read_csv("meta/additional-meta.csv")
meta <- b4 %>% left_join(deets, by=c("Sample ID"="GVL Code"))
```

We have 260 samples. 

```{r}
meta %>% group_by(Location, `Species Common Name`) %>% summarize(count=n())
```
The Mountain, Tahoe and Unidentified are a bit problematic.

```{sh, eval=FALSE}
srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes outputs/200/test260.beagle.gz -K 2 -o outputs/202/ngsadmix-k2 -P 1
srun -p high -t 2:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -likes outputs/200/test260.beagle.gz -K 3 -o outputs/202/ngsadmix-k3 -P 1

for i in {1..10}; do echo $i; $HOME/angsd/misc/NGSadmix -likes outputs/200/test260.beagle.gz -K $i -o outputs/202/ngsadmix-k$i -P 3; done;
```

The Tahoe, mountain, and Unidentified suckers are all mixed together, and the Mountain Sucker should be our outgroup.

See 201 for some splitting by PCA, S_TR_19 looks like a hybrid


## Admix
```{r}
q2<-read_delim("outputs/202/ngsadmix-k2.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2) %>%
  rename(Q1=X1, Q2=X2)

df2<-bind_cols(q2, meta)            

#Hmmm.... Seems we may want to add a column of K=2 so that we can facet later. But we may need to plot separately so that we can all the colors lined up using ggarrange

q2s<-df2 %>% select(`Species Common Name`, Location, `Sample ID`, Q1, Q2) %>% arrange(`Species Common Name`, Location) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 4:5) %>% mutate(K=2)

pops2<-q2s  %>% group_by(`Species Common Name`, Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(`Species Common Name`,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()
```


```{r}
p2 <- ggplot(q2s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops2, x = pops2$Start - 0.5, y=0, xend = pops2$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops2, x = pops2$Stop[length(pops2$Stop)]  + 0.5, y=0, xend= pops2$Stop[length(pops2$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0, xend= pops2$Stop[length(pops2$Stop)], y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0, xend= pops2$Stop[length(pops2$Stop)], y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops2$Stop[length(pops2$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  theme(legend.position = "") +
  scale_x_continuous(breaks=pops2$Position, labels=pops2$`Species Common Name`) +
  theme(axis.text.x=element_text(angle=45))

  
p2

ggsave("outputs/202/k2.jpg")
```

Those eerily 50/50 ones may be the Tahoe suckers.

```{r}
q3<-read_delim("outputs/202/ngsadmix-k3.qopt", delim=" ", col_names=FALSE) %>% select(X1, X2, X3) %>%
  rename(Q1=X1, Q2=X2, Q3=X3)

df3<-bind_cols(meta,q3)            

#Hmmm.... Seems we may want to add a column of K=2 so that we can facet later. But we may need to plot separately so that we can all the colors lined up using ggarrange

q3s<-df3 %>% select(`Species Common Name`, Location, `Sample ID`, Q1, Q2, Q3) %>% arrange(`Species Common Name`, Location) %>%
  mutate(Index=1:n()) %>% gather(key=Ancestry, value=Q, 4:6) %>% mutate(K=3)

pops3<-q3s  %>% group_by(`Species Common Name`, Location) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(`Species Common Name`,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()
```


```{r}
p3 <- ggplot(q3s) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=pops3, x = pops3$Start - 0.5, y=0, xend = pops3$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=pops3, x = pops3$Stop[length(pops3$Stop)]  + 0.5, y=0, xend= pops3$Stop[length(pops3$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0, xend= pops3$Stop[length(pops3$Stop)], y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0, xend= pops3$Stop[length(pops3$Stop)], y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, pops3$Stop[length(pops3$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  theme(legend.position = "") +
  scale_x_continuous(breaks=pops3$Position, labels=pops3$`Species Common Name`) +
  theme(axis.text.x=element_text(angle=45))

  
p3

ggsave("outputs/202/k3.jpg")
```
```{r}
 ggplot(q3s %>% filter(Location %in% c("East Fork Carson River, NV","Poore Creek, CA","Truckee River, NV"))) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  theme(legend.position = "") +
#  scale_x_continuous(breaks=pops3$Position, labels=pops3$`Species Common Name`) +
#  theme(axis.text.x=element_text(angle=45)) +
  facet_grid(`Species Common Name`~Location)

ggsave("outputs/202/k3-facet.jpg", width=16, height=12)

```



```{r}
r<-df3 %>% filter(Q1>0.95) %>% mutate(TipName=`Species Common Name`)
m<-df3 %>% filter(Q2>0.95) %>% mutate(TipName="Mountain Sucker")
t<-df3 %>% filter(Q3>0.95) %>% mutate(TipName="Tahoe Sucker")


```

Previously.
```{r, eval=FALSE}
mountain<-read_tsv("outputs/202/mymountains.tsv") %>% mutate(id="Mountain Sucker") %>% rename(`Sample ID`=sample)
tahoe<-read_tsv("outputs/202/mytahoe.tsv") %>% mutate(id="Tahoe Sucker") %>% rename(`Sample ID`=sample)
renames<- bind_rows(mountain, tahoe)

new<-meta %>% left_join(renames) %>% mutate(TipName=ifelse(`Sample ID` %in% renames$`Sample ID`, id, `Species Common Name`)) %>% filter(`Sample ID` != "S_TR_19" )

new$`Sample ID`<-gsub("-","_",new$`Sample ID`)
new$Location<-gsub(",| ", "_",new$Location)
new$TipName<-gsub(" ","_",new$TipName)
```


Now....
```{r}
new<-bind_rows(r,m,t)
new$`Sample ID`<-gsub("-","_",new$`Sample ID`)
new$Location<-gsub(",| ", "_",new$Location)
new$TipName<-gsub(" ","_",new$TipName)
```


```{r}
treemeta<- new %>% select(`Sample ID`, Location, TipName) %>% group_by(Location, TipName) %>%  
  summarize(Samples=paste0(`Sample ID`, collapse="\t"), `Sample Size` =n()) %>%
  mutate(String=paste0(Location,"_",TipName,":\t",Samples,","))
write_tsv(treemeta %>% ungroup() %>% select(String), "outputs/202/tipnames.txt")
```

Produces a reasonable tree, but, we are missing a lot of C. occidentalis occidentalis.


