---
title: "500-phylogeny"
author: "Mac Campbell"
date: "4/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggtree)
library(ape)
library(treeio)
library(ggrepel)
library(viridis)
```

## Signal in Bagley et al?

Made a 46 taxon alignment with outgroups

```{sh,eval=FALSE}
iqtree -s test.phylip -p test -st DNA -m GTR+G -B 1000  -redo
```

Three partitions:
1	DNA	33	2836	690	1928	GTR	mtDNA
2	DNA	33	839	32	778	GTR	IRBP
3	DNA	13	2250	42	2143	GTR	GHI_RPS7

Partition file causes a crash of iqtree? Running without partitioning.


```{r}
t<-read.tree("outputs/500/test.phylip.contree")
#t<-root(t, c("C_platyrhyn_BYU58618","P_clarkii_MSB49600","P_santa_UAIC12384_01","P_disco_yar_UAIC12776_01_2",
 # "P_discobolus_BYU57986","C_plebius_DAN0521_10","P_nebuliferus"))

og<-c("Myxocyprinus_UAIC11698_01","Car_cyprinus_TU157_01","Car_velifer_TU108_16","Car_carpio_UAIC11219_08","Cyc_elonga_UAIC11371_01","Cyc_merdion_UNL1_30",
             "I_cyprinellus_TU107_15","I_niger_TU121_01")

t<-root(t, og)
t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label > 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label > 75,]

t  +
  geom_point(data=e,  color="gray50", cex=5, alpha=0.75, pch=18) +
  geom_point(data=d,  color="black", cex=5, alpha=0.75, pch=18) +
  geom_tiplab(offset=0.1, align=TRUE, size=3) +
#  geom_nodelab() +
  xlim(0,.5)

ggsave("outputs/500/test.pdf", height=6)
```

Considering making this a timetree....


## Fossils

Fossil MinimumAge Dating
C. asitus 4.5 C. rimiculus from C. snyderi. Due to hybridization... I don't know how useful this one is
C. hyomizon ?



C. oromyzon 4.5 TMRCA of C. bernardini, cahita,latipinnis, insignis (and leopolid)
C. spatulifer 3.0 TMRCA of ardens, macrocheilus, tsiltcoosenis (an Ch. liorus)

A. brevipenne 48.88 TMRCA <- root age of tree?
A. huanensis 37.8 TMRCA of  Ictiobinae

Plesiomyxocyprinus arratiae 39.67 divergence of Myxocyprinus from Cyc

Five calibrations.

## Set up
```{r}
#define ingroup
t$data %>% filter(isTip==TRUE) %>% filter(!(label %in% og)) %>% select(label) %>% write_tsv("outputs/500/ingroup.tsv")
```

Set up relaxed clock dating with mb. After 40 million generations, runs 1,3,4 yield ESS >596. minimum 597 TL{all} with burnin of 10%, tracer v 1.7.2. Loading with mb and rerunning sumt command. `/Users/mac/github/wall-canyon/outputs/500/cui-ui`
	sumt relburnin=yes burninfrac=0.10  nruns=3 contype=allcompat outputname=allcompat;

Now including Ch.cujus

Create nice Meta
```{r, eval=FALSE}
write_csv(t$data %>% filter(isTip=="TRUE") %>% select(label), "meta/time-tree-meta.csv")
```
```{r}
tips<-read_csv("meta/time-tree-meta-edited.csv")
```

```{r}
tt<-read.beast("outputs/500/cui-ui/allcompat.con.tre")

t3<-ggtree(tt)

t3 + geom_nodelab(aes(label=node)) + geom_tiplab() +
  xlim(0,70)
```

```{r}
nodes<- t3$data %>% filter(node %in% c(76,77,78,79,80)) 
nodes$age<-round(as.numeric(nodes$age_median),2)

```

```{r}
up2<-t3 %<+% tips +
  theme_tree2()+
  geom_vline(xintercept=c(3,13,23,33,43), lty=2, lwd=0.5, alpha=0.5) +
  geom_range(range='age_0.95HPD', color='red', alpha=.6, size=2) +
  geom_tiplab(size=3.5, offset=3, aes(label=Name)) +
  geom_tippoint(aes(x=x+.25, fill=`Great Basin`), pch=21, cex=2.5) +
  scale_x_continuous(name="\nTime in Millions of Years Ago", breaks=c(3,13,23,33,43,53), 
                     labels=c(50,40,30,20,10,0),
                     limits=c(0,85))  +
#  geom_label_repel(data=nodes,aes(x=x,y=y,label=age), alpha=0.75) +
  theme(axis.text.x = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14)) +
  scale_fill_viridis_d() +
  geom_cladelab(node=90, "Tahoe Sucker\nand relatives", offset=15) +
  geom_cladelab(node=77, "Wall Canyon Sucker\nand relatives", offset=17) +
  geom_cladelab(node=71, "Mountain Sucker\nand relatives", offset=18) +
  theme(legend.position = "top")

up2
ggsave("outputs/500/time-tree.pdf", width=8.5, height=11)
```

### Ancestral state reconstruction

```{r}
temp<-select(tips, label, `Great Basin`)

target<-t3$data %>% filter(isTip==TRUE) %>% select(label)  

#target<-target%>% dplyr::rename("Seq"="value")

#Sort our data as in tip labels
data<-left_join(target,temp)

ERreconstruction<-ace(data$`Great Basin`,as.phylo(tt), type="discrete", method="ML", model="ER") #or ER
save(ERreconstruction, file="outputs/500/ERreconstruction.rda")
```

```{r}
states<-ERreconstruction$lik.anc %>% as_tibble()
states$node<-rownames(ERreconstruction$lik.anc)
```


```{r}

pies <- nodepie(states, cols=1:2, color=c(Yes=viridis(2)[2], No=viridis(2)[1]), alpha=1)
up3<-inset(up2, pies, width=.08, height=.08)

pdf("outputs/500/equal-rates-ancestral-reconstruction.pdf", width=8, height=11)
up3
dev.off()
```


```{r}
uu<-read.beast("outputs/500/cui-ui/allcompat.con.tre")
uuu<-tree_subset(uu, node=76, levels_back = 0)

ggtree(uuu) +  geom_nodelab(aes(label=node))
u3<-ggtree(uuu) #+ geom_nodelab(aes(label=node))
u3

nodesu <- u3$data  %>% filter(node %in% seq(14,25, by=1))
nodesu$age<-round(as.numeric(nodesu$age_median),2)

xu<-nodesu[3,]$x
yu<-nodesu[3,]$y
zu<-round(unlist(nodesu$height_0.95HPD[3]),2)
lab<-paste0(zu[1],"-",z[2])
dflab<-data_frame(xu,yu,lab)
```

```{r}
u3 %<+% tips +
  geom_range(range='age_0.95HPD', color='red', alpha=.6, size=2) +
  geom_tiplab(size=3, aes(label=Name)) +
  geom_label(data=nodesu,aes(x=x,y=y,label=age), alpha=0.75) +
  geom_label_repel(data=dflab, aes(x=xu, y=yu, label=lab), color="red", alpha=0.75) +
  geom_cladelab(node=15, "Wall Canyon Sucker\nand relatives", offset=8) +
  geom_cladelab(node=23, "Klamath Group", offset=8) +
  geom_cladelab(node=19, "Sacramento Group", offset=8) +
  xlim(0,35)

ggsave("outputs/500/time-tree-subclade.jpg")
```
