---
title: "502-extra-pantosteus"
author: "Mac Campbell"
date: "7/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(treeio)
library(ggtree)
library(ape)
library(viridis)
```

## Including extra Pantosteus
P. lahontan, P. bondi, P. jordani, P. virescens

```{sh, eval=FALSE}
iqtree -s pant.phy -st DNA -m GTR+G -bb 1000  -redo
```

```{r}
tips<-read_csv("meta/time-tree-meta-edited.csv")
```

```{r}
t<-read.tree("outputs/502/pantosteus/pant/pant.phy.contree")
#t<-root(t, c("C_platyrhyn_BYU58618","P_clarkii_MSB49600","P_santa_UAIC12384_01","P_disco_yar_UAIC12776_01_2",
 # "P_discobolus_BYU57986","C_plebius_DAN0521_10","P_nebuliferus"))

#og<-c("Myxocyprinus_UAIC11698_01","Car_cyprinus_TU157_01","Car_velifer_TU108_16","Car_carpio_UAIC11219_08","Cyc_elonga_UAIC11371_01","Cyc_merdion_UNL1_30",
 #            "I_cyprinellus_TU107_15","I_niger_TU121_01")
og<-("Myxocyprinus_UAIC11698_01")
t<-root(t, og)
t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label > 75,]

t  %<+% tips +
  geom_point(data=e,  fill="gray50", cex=3, alpha=0.75, pch=23) +
  geom_point(data=d,  fill="black", cex=3, alpha=0.75, pch=23) +
  geom_tiplab(offset=0.1, align=TRUE, size=3, aes(label=Name)) +
  geom_tippoint(aes(fill=`Great Basin`, shape=`Major Basin`), cex=3, alpha=1) +
  scale_fill_viridis_d() +
  scale_shape_manual(values=c(25,22,23,24,21))+
  guides(fill = guide_legend(override.aes = list(shape=c(21,21), colour="black", 
                                     fill=c(viridis(n=2)[1], viridis(n=2)[2])))) +
#  geom_nodelab() +
  xlim(0,.7) +
  geom_treescale()

ggsave("outputs/502/test.pdf", height=8, width=10)
```


Exporting newick string with FigTree gets me a properly formatted starting tree for mrbayes.


--mail-type=ALL --mail-user
srun -p high -t 1-12:00:00 --nodes=1 /usr/bin/mb mb-pant-40m-1run.nex (118 hrs)

## I revisited this

The tree can be made into a starting tree, under mcmc block:
	startvals Tau=mystarttree; [using starting tree, making sure is specified]

Running on chinook, /Users/mac/Dropbox/ucdavis/suckers/great-basin-suckers-manuscript/tree-search
40 M gens, 3 chains. Trying this out.

This sets a starting tree, not a fixed analysis. Have redone this see tree files in suckers/great-basin-sucker-manuscript/tree-search/run-4

```{r}
tt<-read.beast("~/Dropbox/ucdavis/suckers/great-basin-suckers-manuscript/tree-search/run-4/start-30m.con.tre")

t3<-ggtree(tt)

t3 + geom_nodelab(aes(label=node)) + geom_tiplab() +
  xlim(0,70)
```



```{r}
up2<-t3 %<+% tips +
  theme_tree2()+
  geom_vline(xintercept=c(3,13,23,33,43), lty=2, lwd=0.5, alpha=0.5) +
  geom_range(range='age_0.95HPD', color='red', alpha=.6, size=2) +
  geom_tiplab(size=3.5, offset=3, aes(label=Name)) +
  geom_tippoint(aes(x=x+.25, fill=`Great Basin`, shape=`Major Basin`), cex=2.5) +
  scale_x_continuous(name="\nTime in Millions of Years Ago", breaks=c(3,13,23,33,43,53), 
                     labels=c(50,40,30,20,10,0),
                     limits=c(0,85))  +
#  geom_label_repel(data=nodes,aes(x=x,y=y,label=age), alpha=0.75) +
  theme(axis.text.x = element_text(size=14, face="bold")) +
  theme(axis.title.x = element_text(size=14)) +
  scale_fill_viridis_d() +
 # geom_cladelab(node=90, "Tahoe Sucker\nand relatives", offset=15) +
#  geom_cladelab(node=77, "Wall Canyon Sucker\nand relatives", offset=17) +
#  geom_cladelab(node=71, "Mountain Sucker\nand relatives", offset=18) +
  theme(legend.position = "top") +
  scale_shape_manual(values=c(25,22,23,24,21))+
  guides(fill = guide_legend(override.aes = list(shape=c(21,21), colour="black", 
                                     fill=c(viridis(n=2)[1], viridis(n=2)[2])))) 

up2
ggsave("outputs/502/time-tree.pdf", width=8.5, height=11)
```

### Ancestral state reconstruction

```{r}
temp<-select(tips, label, `Great Basin`)

target<-t3$data %>% filter(isTip==TRUE) %>% select(label)  

#target<-target%>% dplyr::rename("Seq"="value")

#Sort our data as in tip labels
data<-left_join(target,temp)

ERreconstruction<-ace(data$`Great Basin`,as.phylo(tt), type="discrete", method="ML", model="ER") #or ER
save(ERreconstruction, file="outputs/502/ERreconstruction.rda")
```

```{r}
states<-ERreconstruction$lik.anc %>% as_tibble()
states$node<-rownames(ERreconstruction$lik.anc)
```


```{r}

pies <- nodepie(states, cols=1:2, color=c(Yes=viridis(2)[2], No=viridis(2)[1]), alpha=1)
up3<-inset(up2, pies, width=.08, height=.08)

pdf("outputs/502/equal-rates-ancestral-reconstruction.pdf", width=8, height=11)
up3
dev.off()
```

```{r}
ARDreconstruction<-ace(data$`Great Basin`,as.phylo(tt), type="discrete", model="ARD") 
save(ARDreconstruction, file="outputs/502/ARDreconstruction.rda")
```

```{r}
statesa<-ARDreconstruction$lik.anc %>% as_tibble()
statesa$node<-rownames(ARDreconstruction$lik.anc)
```


```{r}

piesa <- nodepie(statesa, cols=1:2, color=c(Yes=viridis(2)[2], No=viridis(2)[1]), alpha=1)
up3a<-inset(up2, piesa, width=.08, height=.08)

pdf("outputs/502/all-rates-different-ancestral-reconstruction.pdf", width=8, height=11)
up3a
dev.off()
```