---
title: "502-extra-pantosteus"
author: "Mac Campbell"
date: "7/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggtree)
library(ape)
library(viridis)
```

## Including extra Pantosteus
P. lahontan, P. bondi, P. jordani, P. virescens

```{sh, eval=FALSE}
iqtree -s pant.phy -st DNA -m GTR+G -bb 1000  -redo
```

```{r}
tips<-read_csv("meta/time-tree-meta-edited.csv")
```

```{r}
t<-read.tree("outputs/502/pantosteus/pant/pant.phy.contree")
#t<-root(t, c("C_platyrhyn_BYU58618","P_clarkii_MSB49600","P_santa_UAIC12384_01","P_disco_yar_UAIC12776_01_2",
 # "P_discobolus_BYU57986","C_plebius_DAN0521_10","P_nebuliferus"))

#og<-c("Myxocyprinus_UAIC11698_01","Car_cyprinus_TU157_01","Car_velifer_TU108_16","Car_carpio_UAIC11219_08","Cyc_elonga_UAIC11371_01","Cyc_merdion_UNL1_30",
 #            "I_cyprinellus_TU107_15","I_niger_TU121_01")
og<-("Myxocyprinus_UAIC11698_01")
t<-root(t, og)
t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label > 75,]

t  %<+% tips +
  geom_point(data=e,  fill="gray50", cex=3, alpha=0.75, pch=23) +
  geom_point(data=d,  fill="black", cex=3, alpha=0.75, pch=23) +
  geom_tiplab(offset=0.1, align=TRUE, size=3, aes(label=Name)) +
  geom_tippoint(aes(fill=`Great Basin`, shape=`Major Basin`), cex=3, alpha=1) +
  scale_fill_viridis_d() +
  scale_shape_manual(values=c(25,22,23,24,21))+
  guides(fill = guide_legend(override.aes = list(shape=c(21,21), colour="black", 
                                     fill=c(viridis(n=2)[1], viridis(n=2)[2])))) +
#  geom_nodelab() +
  xlim(0,.7) +
  geom_treescale()

ggsave("outputs/502/test.pdf", height=8, width=10)
```


Exporting newick string with FigTree gets me a properly formatted starting tree for mrbayes.


--mail-type=ALL --mail-user
srun -p high -t 1-12:00:00 --nodes=1 /usr/bin/mb mb-pant-40m-1run.nex (118 hrs)

and four runs together for comparison (518hrs?)

### Results

A single 40M run has sufficient ess. Putting treefiles in outputs/502/summary

Need to be named like so: 
temp.t.run1.p      
temp.t.run1.t    
temp.t.run2.p    
temp.t.run2.t   
temp.t.run3.p   
temp.t.run3.t   

sumt relburnin=yes burninfrac=0.10  nruns=3 contype=allcompat outputname=allcompat;

see temp.t, can execute like "mb temp.t"