---
title: "602-abgd"
author: "Mac Campbell"
date: "7/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggtree)
library(phytools)
```

cytb.

(base) Macs-MacBook-Pro-2:602 mac$ grep ">" cytb.afas 
>MH603006.1 Catostomus sp. 'Wall Canyon'
>JX488812.1 Catostomus sp. 'Wall Canyon'
>JX488813.1 Catostomus sp. 'Wall Canyon'
>JX488814.1 Catostomus warnerensis
>KU697915.1 Catostomus warnerensis
>JX488815.1 Catostomus warnerensis 
>JX488785.1 Catostomus fumeiventris
>MH603022.1:1 Catostomus fumeiventris
>JX488784.1 Catostomus fumeiventris

in 602: ../temp/Abgd/abgd -a cytb.afas 
../temp/Abgd/abgd -a nd2.afas
>MH603026.1:1-1047 Catostomus sp.
>JX488882.1:1-1047 Catostomus sp.
>JX488883.1:1-1047 Catostomus sp.
>JX488884.1:1-1047 Catostomus warnerensis
>KU697943.1:1-1047 Catostomus warnerensis
>JX488885.1:1-1047 Catostomus warnerensis
>KU697962.1:1-1047 Chasmistes cujus
>JX488853.1:1-1047 Catostomus fumeiventris
>JX488854.1:1-1047 Catostomus fumeiventris
>MH603042.1:1-1047 Catostomus fumeiventris

~/Dropbox/bin/shortenNamesMac.pl nd2.afas > nd2-shortnames.afas
../temp/Abgd/abgd -a nd2-shortnames.afas 

../temp/Abgd/abgd -a nd2-renamed.afas 

~/Dropbox/bin/shortenNamesMac.pl nd2-Sac+Klam+Wall.txt > nd2-Sac+Klam+Wall.fas
mafft nd2-Sac+Klam+Wall.fas > nd2-Sac+Klam+Wall.afas
 ../temp/Abgd/abgd -a nd2-Sac+Klam+Wall.afas
 
```{r}
tree<-read.tree("outputs/602/nd2-renamed.part.1.tree")
tree<-midpoint.root(tree)
```

```{r}
ggtree(tree) +
  geom_tiplab() +
  geom_treescale()+
xlim(0,.1)

ggsave("outputs/602/cytb-abgd-tree.pdf")
ggsave("outputs/602/cytb-abgd-tree.jpg")
```
     
https://bioinfo.mnhn.fr/abi/public/asap/asapweb.html
ASAP

saved in outputs/602